Appendix

### 2023-05-02 writing/Manuscript_2022.Rmd
updates to submission .rmd

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
library(here)
library(assertthat)
library(langcog)
library(ggthemes)
library(knitr)
library(lmerTest)
library(lme4)
library(xtable)
library(viridis)
library(papaja)
```

@@

@@

>>>>

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
library(here)
library(assertthat)
library(langcog)
library(ggthemes)
library(knitr)
library(lmerTest)
library(lme4)
library(xtable)
library(viridis)
library(papaja)
library(NatParksPalettes)
```

@@

## Extra models after peer-review

### composite effort score
```{r}

d <- d %>%
  ungroup %>%
  mutate(avg_tracing_score_scaled = scale(avg_tracing_score),
         mean_intensity_scaled = scale(mean_intensity),
         draw_duration_scaled = scale(draw_duration)) %>%
  mutate(effort_compiled = avg_tracing_score_scaled + mean_intensity_scaled + draw_duration_scaled)
```

```{r}

full_model_with_effort_combined <- glmer(cbind(num_correct, num_incorrect) ~ condition*scale(age_numeric)*site +
                      scale(avg_tracing_score) +
                      scale(effort_compiled) + 
                      (condition | unique_ids) +
                      (condition*scale(age_numeric) | category),
      data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

full_model_with_effort_combined_out = summary(full_model_with_effort_combined)

```{R}
tracing_score_by <- glmer(cbind(num_correct, num_incorrect) ~ condition*scale(age_numeric)*site +
                      scale(avg_tracing_score) +
                      scale(effort_compiled) + 
                      (condition | unique_ids) +
                      (condition*scale(age_numeric) | category),
      data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
```

@@

```{r}
lmer(data = tracing_scores_indiv, avg_tracing_score ~ scale(age_numeric)*site + (1|unique_ids))
```
